\vspace{1.0cm} \huge \bf Supplemental information:\\ \LARGE Reassortment between influenza B lineages and the emergence of a co-adapted PB1-PB2-HA gene complex

### 2014-08-07 fluB_supp.tex
Add more dTMRCA explanation to supp.

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.85\textwidth]{figures/InfB_methodSpeciesTree.pdf}
	\caption{\textbf{Calculating $\dtmrca$ from a species tree perspective.}
Consider an organism that has diverged into 3 taxa (A, B, C) with a genome comprised of 3 segments (blue, green and red).
Due to reassortments taxa A and B share a slightly more recent TMRCA in the red segment, likewise for taxa B and C in the green segment.
By comparing differences in TMRCAs between taxa A-B, A-C and B-C in blue, red and green segments we would find that the red segment has a lower `reassortment distance' (X) than the green segment (Y).
}
	\label{speciesTree}
\end{figure}

>>>>

\begin{figure}[h]
	\centering	
	\includegraphics[width=0.85\textwidth]{figures/InfB_methodSpeciesTree.pdf}
	\caption{\textbf{Calculating $\dtmrca$ from a species tree perspective.}
Consider an organism that has diverged into 3 taxa (A, B, C) with a genome comprised of 3 segments (blue, green and red).
Due to reassortments taxa A and B share a slightly more recent TMRCA in the red segment, likewise for taxa B and C in the green segment.
By comparing differences in TMRCAs between taxa A-B, A-C and B-C in blue, red and green segments we would find that the red segment has a lower `reassortment distance' (X) than the green segment (Y).
In the absence of reassortment we expect every segment in the genome to have the same tree, \textit{i.e.} the tree of every segment should recapitulate the `virus' tree (analogous to `species' trees in diploid population genetics), including the dates of nodes.
Due to population bottlenecks influenza viruses go through each year we expect strains isolated at any given time to have descended from a single recent virus genome.
This descent from a single genome should therefore be reflected in the TMRCAs of all segments, the only exception being reassortment, which will dramatically alter the TMRCAs of the reassorted segment tree with respect to the background onto which it is reassorting.
}
	\label{speciesTree}
\end{figure}
